EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-18 draft.tex
Update Conclusions

As a proof-of-concept, we present a brief experiment that is deployed in three
distinct environments, taking advantage that as a container-based application,
EvoSwarm describes the deployment of loosely coupled processes in a consistent
and portable way.

The term cloud-native describes these container-based
environments because we can deploy them on an infrastructure that abstracts the
underlying compute, storage, and networking primitives. This infrastructure does not
need to be a cloud provider; it could be a developer's laptop, a single server,
or a production environment. When we deploy a cloud-native application to a
cloud provider, we have some more options to choose:

@@

In this paper, we have presented the EvoSwarm framework that implements an
event-based, cloud-native architecture suitable for hosting multi-population
optimization algorithms. The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy to develop and deploy
multi-algorithm distributed experiments. The model is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data. We compared the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature. We
found that it is best suited for asynchronous multi-population algorithms.

We proposed a new methodology for the reproducible deployment and execution of
multiple experiments by specifying the infrastructure as part of an experiment
definition in both local or cloud environments. We presented the workflow of an
experiment's entire life-cycle viewed from the perspective of developers and
researchers. We tested the deployment on both local and Amazon's Elastic
Container Service.

@@

First, we focused on knowing how scaling is related to the number of populations
and workers in the system. This experiment concludes that there is an
interesting interplay, with the most benefit obtained with a number of
populations near-equal to the number of workers, which brings performance gains.
Also, we found that for lower dimensions, there is an advantage in using fewer
populations.

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms. We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework for continuous functions.
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The ensemble
achieved better results and, in most cases, needed fewer evaluations.

>>>>

EvoSwarm describes the deployment of loosely coupled processes in a consistent
and portable way. The term cloud-native describes these container-based
environments because we can deploy them on an infrastructure that abstracts the
underlying compute, storage, and networking primitives. This infrastructure does
not need to be a cloud provider; it could be a developer's laptop, a single
server, or a production environment. In this section, we answer the following
question:

Can EvoSwarm as a cloud-native, container-based application be deployed locally
or in the cloud by specifying the configuration of container images and
resources in an orchestration service?

To prove this question, we present a brief optimization experiment that is
deployed in three distinct environments, taking advantage of it as a
container-based application. When we deploy a cloud-native application to a cloud provider, we have some more
options to choose:

@@

In this paper, we have presented the EvoSwarm framework for 
the reproducible execution of experiments with an event-based, cloud-native architecture 
suitable for hosting multi-population, multi-algorithm optimization algorithms. % reproducible? It's in the title - JJ Yes - M
The framework is based in industry-standard development
tools such as Docker and Docker Compose, making it easy for scientists and practitioners to develop and deploy
multi-algorithm distributed experiments. The model is based on the asynchronous
exchange of messages between stateless functions that react to a continuous
stream of data. We show the differences of the message-driven architecture we presented against
four other proposals for multi-population algorithms found in the literature, and highlight the 
advantages for conducting asynchronous multi-population algorithms.
% But it's not a practical comparison, but a theoretical one. Show the differences instead of compare? - JJ - Ok 
% We found that it is best suited for asynchronous multi-population algorithms. % This is not really proved. You chose, you didn't find - JJ
% Ok, I put it in the same package - M

We proposed a new methodology for the reproducible deployment and execution of
multiple experiments by specifying the infrastructure as part of an experiment
definition in both local or cloud environments. We presented the workflow of an
experiment's entire life-cycle viewed from the perspective of developers and
researchers.  % and we proved... Remember the experimental hypothesis - JJ - Ok - 
We tested the deployment of an experiment on Amazon's Elastic
Container Service, and proved that as cloud-native, container-based application,
EvoSwarm could be deployed locally or in the cloud by specifying the configuration 
of container images and resources in an orchestration service.

@@

First, we focused on knowing how scaling is related to the number of populations
and workers in the system. This experiment concludes that there is an
interesting interplay, with the most benefit obtained with a number of
populations slightly above the number of workers, which brings performance gains 
in terms of execution speed with experiments taking less time because
evaluations are shared between different workers. % of what kind? - JJ
Also, we found that for lower dimensions, there is an advantage in using fewer
populations.

A second experiment centered on evaluating the algorithmic benefits (experiments
taking less time because they need fewer evaluations) of distributed
multi-algorithm algorithms. We compared the homogeneous and an ensemble of
multi-populations, using Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) using the COCO benchmark framework 
for visualization and definition of the optimization problems. % as a visualization device? - JJ  
% we also used their functions -M
We found that the set-up of these algorithms has a significant influence on
their results since diversity is essential for their performance. The ensemble
achieved better results and, in most cases, needed fewer evaluations.
